---
title: "The paradox of climate policy diffusion"
author: "Ivan Savin, Philipp Mundt and Margherita Bellanca"
date: '2025-01-20'
output: word_document
---

```{r setup, include=FALSE}

rm(list=ls())
knitr::opts_chunk$set(fig.width=10, fig.height=15,dpi=500,warning = FALSE, message = FALSE) #10 15 
mcFr2 <- function(model, init) {
  return( list( "mcf" = 1 - logLik(model)[[1]]/init ) )
}

library("plm")
library("pglm")
library("corrplot")
library("domir")
library("fastshap")
library("ggplot2")
library("performance")
library("plyr")
library ("lmtest")
library("sandwich")
library("lfe")
library("shapley")
library("DescTools")

#surpress warnings
defaultW <- getOption("warn")
options(warn = -1)

# Controls <- read.csv("D:/Projects/2_Working Papers/Margherita/Controls1990updated.csv")
# Controls <- pdata.frame(Controls, index=c("ISO","Year"))


Flow <- read.csv("D:/Projects/2_Working Papers/Margherita/DataPanelFormatFlowV29.csv")
Flow <- pdata.frame(Flow, index=c("ISO","Year"))
Flow <- transform(Flow, Trend = as.numeric(Year)) 
#FlowM <- merge(x=Flow,y=Controls, by.x=c("ISO","Year"), by.y=c("ISO","Year"))
FlowM <- Flow
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Count.Lag = c(NA, SpatialLag.Count[-length(SpatialLag.Count)]))
FlowM <- ddply(FlowM, .(ISO), transform, Count.Lag = c(NA, Count[-length(Count)]))
FlowM <- ddply(FlowM, .(ISO), transform, Market.Instr.Lag = c(NA, Market.Instr[-length(Market.Instr)]))
FlowM <- ddply(FlowM, .(ISO), transform, Non.Market.Instr.Lag = c(NA, Non.Market.Instr[-length(Non.Market.Instr)]))
FlowM <- ddply(FlowM, .(ISO), transform, TechSup.Instr.Lag = c(NA, TechSup.Instr[-length(TechSup.Instr)]))

# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Barrier.removal.Lag = c(NA, SpatialLag.Barrier.removal[-length(SpatialLag.Barrier.removal)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Climate.strategy.Lag = c(NA, SpatialLag.Climate.strategy[-length(SpatialLag.Climate.strategy)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Economic.instruments.Lag = c(NA, SpatialLag.Economic.instruments[-length(SpatialLag.Economic.instruments)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Information.and.education.Lag = c(NA, SpatialLag.Information.and.education[-length(SpatialLag.Information.and.education)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Policy.support.Lag = c(NA, SpatialLag.Policy.support[-length(SpatialLag.Policy.support)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Regulatory.Instruments.Lag = c( NA, SpatialLag.Regulatory.Instruments[-length(SpatialLag.Regulatory.Instruments)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.RDD.Lag = c( NA, SpatialLag.RDD[-length(SpatialLag.RDD)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Target.Lag = c( NA, SpatialLag.Target[-length(SpatialLag.Target)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Voluntary.approaches.Lag = c( NA, SpatialLag.Voluntary.approaches[-length(SpatialLag.Voluntary.approaches)]))

FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Market.Instr.Lag = c( NA, SpatialLag.Market.Instr[-length(SpatialLag.Market.Instr)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.Non.Market.Instr.Lag = c( NA, SpatialLag.Non.Market.Instr[-length(SpatialLag.Non.Market.Instr)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.TechSup.Instr.Lag = c( NA, SpatialLag.TechSup.Instr[-length(SpatialLag.TechSup.Instr)]))

FlowM$NorthSouth<-matrix(0,length(FlowM$ISO),1)
FlowM$NorthSouth[which(FlowM$ISO %in% c("FRA","GBR","DEU","JPN", "KOR","USA","AUS","ITA","ESP", "CAN"))]<-1
table(FlowM$NorthSouth)
summary(FlowM$NorthSouth)

colnames(FlowM)[12]<-"Gini"
keycountries<-c("BRA","IDN","IND","MEX","RUS","TUR","ZAF","FRA","GBR","DEU","JPN", "KOR","USA","AUS","ITA","ESP", "CAN","CHN","NZL", "CHL","CHE")
#"NOR"
```




```{r EPS, echo=FALSE, warning=FALSE}
# 
# Flow$EPS<-as.numeric(Flow$EPS)
# FlowM$EPS<-as.numeric(FlowM$EPS)

EPSplot<-matrix(0,25,23)
EPSplot<-as.data.frame(EPSplot)
colnames(EPSplot)<-c("Year", "AUS", "BRA", "CAN", "CHE", "CHL","CHN", "DEU", "ESP", "FRA", "GBR", "IDN", "IND", "ITA", "JPN", "KOR", "MEX", "NOR", "NZL", "RUS", "TUR", "USA", "ZAF")
EPSplot$Year<-1996:2020

j<-1
for (i in unique(Flow$ISO)){
  
  EPSplot[,(j+1)]<-Flow$EPS_MKT_CC[(25*(j-1)+1):(25*j)]
j<-j+1
}
library(RColorBrewer)
set.seed(333)
n <- 23
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
col_vector=sample(col_vector, n)
countries <-c("AUS", "BRA", "CAN", "CHE", "CHL","CHN", "DEU", "ESP", "FRA", "GBR", "IDN", "IND", "ITA", "JPN", "KOR", "MEX", "NOR", "NZL", "RUS", "TUR", "USA", "ZAF")

# matplot(EPSplot[,1], EPSplot[,c(2:23)], type = "l", lty = 1,
#         xlab = "Year", col=col_vector,
#         ylab = "EPS", main = "EPS across countries")
# legend("topleft", legend =countries,
#        col = col_vector, lty = 1)
# 
# EPSplot<-EPSplot[,-c(2,22)]
# countries<-countries[-c(2,22)]
par(mfrow = c(6,4) ,mar=c(2,2,1.5,1))
for (j in 1:22){
  matplot(EPSplot[,1], EPSplot[,c(j+1)], type = "l", lty = 1, 
        col=col_vector[j],xlab="",
        ylab = "EPS", main = countries[j],
        ylim=c(0,5))
}



###EPS CC
EPS_plot<-matrix(0,25,23)
EPS_plot<-as.data.frame(EPS_plot)
colnames(EPS_plot)<-c("Year", "AUS", "BRA", "CAN", "CHE", "CHL","CHN", "DEU", "ESP", "FRA", "GBR", "IDN", "IND", "ITA", "JPN", "KOR", "MEX", "NOR", "NZL", "RUS", "TUR", "USA", "ZAF")
EPS_plot$Year<-1996:2020

par(mfrow = c(5,5) ,mar=c(2,2,1.5,1))

j<-1
for (i in unique(Flow$ISO)){
  
  EPS_plot[,(j+1)]<-Flow$EPS_CC[(25*(j-1)+1):(25*j)]
j<-j+1
}

# EPS_plot<-EPS_plot[,-c(2,22)]

for (j in 1:22){
  matplot(EPS_plot[,1], EPS_plot[,c(j+1)], type = "l", lty = 1, 
        col=col_vector[j],
        ylab = "EPS", main = countries[j],
        ylim=c(0,5))
}




#Panel
FlowM <- ddply(FlowM, .(ISO), transform, EPS_CC.Lag = c(NA, EPS[-length(EPS_CC)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_CC.Lag = c(NA, SpatialLag.EPS_CC[-length(SpatialLag.EPS_CC)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_MKT_CC.Lag = c(NA, SpatialLag.EPS_MKT_CC[-length(SpatialLag.EPS_MKT_CC)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_NMKT_CC.Lag = c(NA, SpatialLag.EPS_NMKT_CC[-length(SpatialLag.EPS_NMKT_CC)]))
FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.TECHSUP.Lag = c(NA, SpatialLag.TECHSUP[-length(SpatialLag.TECHSUP)]))


# 
# FlowM <- ddply(FlowM, .(ISO), transform, EPS_CC.Lag = c(NA, EPS_CC[-length(EPS_CC)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_CC.Lag = c(NA, SpatialLag.EPS_CC[-length(SpatialLag.EPS_CC)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_MKT_CC.Lag = c(NA, SpatialLag.EPS_MKT_CC[-length(SpatialLag.EPS_MKT_CC)]))
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_NMKT_CC.Lag = c(NA, SpatialLag.EPS_NMKT_CC[-length(SpatialLag.EPS_NMKT_CC)]))
# 
# FlowM <- ddply(FlowM, .(ISO), transform, SpatialLag.EPS_CC_Difference.Lag = c(NA, SpatialLag.EPS_CC_Difference[-length(SpatialLag.EPS_CC_Difference)]))




regEPS <- plm(EPS_CC ~ EPS_CC.Lag + SpatialLag.EPS_CC.Lag + yrsoffc + eiec + gov_left + gov_right + GovEffectiveness + GDP_PC + GHG_Int + Gini, data=FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
res <- summary(regEPS)
res
res_robust<-coeftest(regEPS, vcov.=vcovHC(regEPS, method="white2", type="HC1"))
res_robust

write.csv(res_robust, file="D:/Projects/2_Working Papers/Margherita/Revision NComm 2025/EPS_CC_CPDEPS_lag.csv")




reg_pformula <- function(factors) {
    if (length(factors) == 0) return(0)
    formula <- paste("EPS_CC ~", paste(factors, collapse = "+"))
    m <- plm(formula, data = FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
    summary(m)$r.squared[1]
}
Rpseudo<-reg_pformula(c("EPS_CC.Lag", "SpatialLag.EPS_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right",  "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"))
test<-shapley(reg_pformula, c("EPS_CC.Lag", "SpatialLag.EPS_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"), silent = TRUE)
test$value<-test$value
print(Rpseudo)
test


```


```{r EPS MKT, echo=FALSE, warning=FALSE}


FlowM <- ddply(FlowM, .(ISO), transform, EPS_MKT_CC.Lag = c(NA, EPS_MKT_CC[-length(EPS_MKT_CC)]))

#Panel
regEPS_MKT <-plm(EPS_MKT_CC ~ EPS_MKT_CC.Lag + SpatialLag.EPS_MKT_CC.Lag + yrsoffc + eiec + gov_left + gov_right +  GovEffectiveness + GDP_PC + GHG_Int + Gini, data=FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
res <- summary(regEPS_MKT)
res
res_robust<-coeftest(regEPS_MKT, vcov.=vcovHC(regEPS_MKT, method="white2", type="HC1"))
res_robust

write.csv(res_robust, file="D:/Projects/2_Working Papers/Margherita/Revision NComm 2025/EPS_MKT_CC_CPDEPS_lag.csv")



reg_pformula <- function(factors) {
    if (length(factors) == 0) return(0)
    formula <- paste("EPS_MKT_CC ~", paste(factors, collapse = "+"))
    m <- plm(formula, data = FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
    summary(m)$r.squared[1]
}
Rpseudo<-reg_pformula(c("EPS_MKT_CC.Lag", "SpatialLag.EPS_MKT_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"))
test<-shapley(reg_pformula, c("EPS_MKT_CC.Lag", "SpatialLag.EPS_MKT_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"), silent = TRUE)
test$value<-test$value
print(Rpseudo)
test

```



```{r EPS NMKT, echo=FALSE, warning=FALSE}

FlowM <- ddply(FlowM, .(ISO), transform, EPS_NMKT_CC.Lag = c(NA, EPS_NMKT_CC[-length(EPS_NMKT_CC)]))
# 
# #CC
# FlowM <- ddply(FlowM, .(ISO), transform, EPS_NMKT_CC.Lag = c(NA, EPS_NMKT_CC[-length(EPS_NMKT_CC)]))

#Panel
regEPS_NMKT <-plm(EPS_NMKT_CC ~ EPS_NMKT_CC.Lag + SpatialLag.EPS_NMKT_CC.Lag + yrsoffc + eiec + gov_left + gov_right + GovEffectiveness + GDP_PC + GHG_Int + Gini, data=FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
res <- summary(regEPS_NMKT)
res
res_robust<-coeftest(regEPS_NMKT, vcov.=vcovHC(regEPS_NMKT, method="white2", type="HC1"))
res_robust

write.csv(res_robust, file="D:/Projects/2_Working Papers/Margherita/Revision NComm 2025/EPS_NMKT_CC_CPDEPS_lag.csv")

reg_pformula <- function(factors) {
    if (length(factors) == 0) return(0)
    formula <- paste("EPS_NMKT_CC ~", paste(factors, collapse = "+"))
    m <- plm(formula, data = FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
    summary(m)$r.squared[1]
}
Rpseudo<-reg_pformula(c("EPS_NMKT_CC.Lag","SpatialLag.EPS_NMKT_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"))
test<-shapley(reg_pformula, c("EPS_NMKT_CC.Lag","SpatialLag.EPS_NMKT_CC.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"), silent = TRUE)
test$value<-test$value
print(Rpseudo)
test


```

```{r EPS TECHSUP, echo=FALSE, warning=FALSE}

FlowM <- ddply(FlowM, .(ISO), transform, TECHSUP.Lag = c(NA, TECHSUP[-length(TECHSUP)]))


#Panel
regTECHSUP <-plm(TECHSUP ~ TECHSUP.Lag + SpatialLag.TECHSUP.Lag + yrsoffc + eiec + gov_left + gov_right + GovEffectiveness + GDP_PC + GHG_Int + Gini, data=FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
res <- summary(regTECHSUP)
res
res_robust<-coeftest(regTECHSUP, vcov.=vcovHC(regTECHSUP, method="white2", type="HC1"))
res_robust

write.csv(res_robust, file="D:/Projects/2_Working Papers/Margherita/Revision NComm 2025/EPS_TECHSUP_CC_CPDEPS_lag.csv")

reg_pformula <- function(factors) {
    if (length(factors) == 0) return(0)
    formula <- paste("TECHSUP ~", paste(factors, collapse = "+"))
    m <- plm(formula, data = FlowM, index=c("ISO","Year"), model = "within", effect = "twoways")
    summary(m)$r.squared[1]
}
Rpseudo<-reg_pformula(c("TECHSUP.Lag","SpatialLag.TECHSUP.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"))
test<-shapley(reg_pformula, c("TECHSUP.Lag","SpatialLag.TECHSUP.Lag", "yrsoffc", "eiec", "gov_left", "gov_right", "GovEffectiveness", "GDP_PC", "GHG_Int", "Gini"), silent = TRUE)
test$value<-test$value
print(Rpseudo)
test


```


At the beginning we observe most countries starting low in climate policies
```{r Maps in 1991, echo=FALSE, warning=FALSE}
dataset <- read.csv("D:/Projects/2_Working Papers/Margherita/DataPanelFormatFlowV29.csv")

focus_year<-1996 #between 1990 and 2020
 
focus_indicator<-"Count" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange

data_map<-dataset[c(focus_indicator,"Year","ISO")]

data_map<-data_map[which(data_map$Year==focus_year),]

library(rnaturalearth)
library(rnaturalearthdata)
library(ggplot2)
library(dplyr)

# Load country boundaries for Africa
world<- ne_countries(scale = "medium", returnclass = "sf")


# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = Count)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "Policy Count") +
  theme_minimal() +
  labs(title = "Number of new policies introduced in 1996")


scatterplot<-data_map[,c(1,3)]



focus_indicator<-"EPS_CC" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange
data_map<-dataset[c(focus_indicator,"Year","ISO")]
data_map<-data_map[which(data_map$Year==focus_year),]

# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = EPS_CC)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "EPS") +
  theme_minimal() +
  labs(title = "Stringency of climate policy (EPS_CC) in 1996")

scatterplot<-cbind(scatterplot, data_map$EPS_CC)

colnames(scatterplot)<-c("Count","ISO","EPS_CC")

library(ggrepel)

ggplot(scatterplot, aes(Count,EPS_CC)) +
  geom_point() +
  geom_text_repel(aes(label = ISO))+
  ggtitle("Count vs EPS in 1996")


```


But over time two main clusters develop in EPS (but not in policy count): G7 + Korea + Spain + Australia (developed) vs BRICS + Mexico + Indonesia + Turkey  + presumably Saudi Arabia and Argentina  (developing).
In policy count the countries are much more alike.

```{r Maps in 2005, echo=FALSE, warning=FALSE}

focus_year<-2005 #between 1990 and 2020
 
focus_indicator<-"Count" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange

data_map<-dataset[c(focus_indicator,"Year","ISO")]

data_map<-data_map[which(data_map$Year==focus_year),]

# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = Count)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "Policy Count") +
  theme_minimal() +
  labs(title = "Number of new policies introduced in 2005")


scatterplot<-data_map[,c(1,3)]



focus_indicator<-"EPS_CC" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange
data_map<-dataset[c(focus_indicator,"Year","ISO")]
data_map<-data_map[which(data_map$Year==focus_year),]

# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = EPS_CC)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "EPS") +
  theme_minimal() +
  labs(title = "Stringency of climate policy (EPS_CC) in 2005")

scatterplot<-cbind(scatterplot, data_map$EPS_CC)

colnames(scatterplot)<-c("Count","ISO","EPS_CC")

library(ggrepel)

ggplot(scatterplot, aes(Count,EPS_CC)) +
  geom_point() +
  geom_text_repel(aes(label = ISO))+
  ggtitle("Count vs EPS in 2005")

```


Closer to 2020 the gap between the two clusters in EPS starts to reduce, notably China, India and Turkey increase policy stringency
```{r Maps in 2020, echo=FALSE, warning=FALSE}


focus_year<-2020 #between 1990 and 2020
 
focus_indicator<-"Count" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange

data_map<-dataset[c(focus_indicator,"Year","ISO")]

data_map<-data_map[which(data_map$Year==focus_year),]

# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = Count)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "Policy Count") +
  theme_minimal() +
  labs(title = "Number of new policies introduced in 2020")


scatterplot<-data_map[,c(1,3)]



focus_indicator<-"EPS_CC" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange
data_map<-dataset[c(focus_indicator,"Year","ISO")]
data_map<-data_map[which(data_map$Year==focus_year),]

# Merge startup counts with country boundaries
map_with_data <- left_join(world, data_map, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = EPS_CC)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "EPS") +
  theme_minimal() +
  labs(title = "Stringency of climate policy (EPS_CC) in 2020")

scatterplot<-cbind(scatterplot, data_map$EPS_CC)

colnames(scatterplot)<-c("Count","ISO","EPS_CC")

library(ggrepel)

ggplot(scatterplot, aes(Count,EPS_CC)) +
  geom_point() +
  geom_text_repel(aes(label = ISO))+
  ggtitle("Count vs EPS in 2020")

```


And this is a summary over all years as average
```{r Maps average over years, echo=FALSE, warning=FALSE}


focus_indicator<-"Count" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange

data_map<-dataset[c(focus_indicator,"Year","ISO")]

myData <- aggregate(data_map$Count,
                    by = list(data_map$ISO),
                    FUN = function(x) c(mean = mean(x), sd = sd(x),n= length(x)))
myData <- do.call(data.frame, myData)

colnames(myData)<-c("ISO","meanCount","sd","n")


# Merge startup counts with country boundaries
map_with_data <- left_join(world, myData , by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = meanCount)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "Average policy count") +
  theme_minimal() +
  labs(title = "Number of new policies introduced in 1995-2020")


scatterplot<-myData [,c(1,2)]


focus_indicator<-"EPS_CC" # Count	Barrier.removal	Climate.strategy	Economic.instruments	Information.and.education	Policy.support	Regulatory.Instruments	RDD	Target	Voluntary.approaches	Market.Instr	Non.Market.Instr	TechSup.Instr	EPS	EPS_MKT	EPS_NMKT	TECHSUP	TaxPer	TaxValue	PercentageChange
data_map<-dataset[c(focus_indicator,"Year","ISO")]


myData <- aggregate(data_map$EPS_CC,
                    by = list(data_map$ISO),
                    FUN = function(x) c(mean = mean(x,na.rm=TRUE), sd = sd(x,na.rm=TRUE),n= length(x)))
myData <- do.call(data.frame, myData)

colnames(myData)<-c("ISO","meanEPS_CC","sd","n")


# Merge startup counts with country boundaries
map_with_data <- left_join(world, myData, by = c("iso_a3_eh" = "ISO"))


# Plot the map
ggplot(data = map_with_data) +
  geom_sf(aes(fill = meanEPS_CC)) +
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "grey", name = "EPS_CC") +
  theme_minimal() +
  labs(title = "Stringency of climate policy (EPS_CC) in 1995-2020")

scatterplot<-cbind(scatterplot, myData$meanEPS_CC)

colnames(scatterplot)<-c("ISO","meanCount","meanEPS_CC")


ggplot(scatterplot, aes(meanCount,meanEPS_CC)) +
  geom_point() +
  geom_text_repel(aes(label = ISO))+
  ggtitle("")+
  xlab("Average policy count")+
  ylab("Average EPS_CC")


cor.test(dataset$Count,dataset$EPS_CC)

# 
# ggplot(dataset, aes(Count,EPS)) +
#   geom_point() +
#  # geom_text_repel(aes(label = ISO))+
#   geom_point(aes(colour = ISO))
```